Paper_analyses

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
<!--   group_by(stimIAPS, ssid,valence_self)%>% -->
<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
<!--   ggplot(aes(stimIAPS, arousal, color = valence_self))+ -->
<!--   # geom_point()+ -->
<!--   stat_summary(funy = mean, geom = 'pointrange') -->

>>>>

a few checks on stim by ratings 
```{r eval=FALSE, include=FALSE}
<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
<!--   group_by(stimIAPS, ssid,valence_self)%>% -->
<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
<!--   ggplot(aes(stimIAPS, arousal, color = valence_self))+ -->
<!--   # geom_point()+ -->
<!--   stat_summary(funy = mean, geom = 'pointrange') -->
